---
title: "Notebook 4"
author: "Group 10 (Umar, Cory, Caroline, Benji)"
date: "10/9/2022"
output:
  pdf_document: default
  html_notebook: default
---


# Introduction

## About this set 
[Bank marketing](https://archive.ics.uci.edu/ml/datasets/Bank+Marketing) was downloaded from archive.ics.uci.edu. The set includes direct marketing campaign phone calls from a portugese banking institution. 


### 80:20 Training and Test Sets 

In the code block below users can obtain the code used to read a dataset in csv format and install the accompanying tools to split dataset into training and testing sets. 

```{r}
# Code to split data into training and test datasets

# Importing data sets

library(caret)
library(class)
library(tree)
library(MASS)


data <- read.csv("bank-additional-full.csv")
data <- subset(data, select = -c(pdays, duration, default))
replace_unknowns <- function(df) {
  for(col in colnames(df)) {
    if(has_unknown(df,col)) {
      n_unk <- sum(df[,col]=="unknown")
      idx <- which(df[,col]=="unknown")
      df[idx,col] <- sample(col[!col=="unknown"],n_unk,replace=TRUE)
    }
  }
  df
}
cats <- names(data)[sapply(data,is.character)]
encode <- function(df,col) {
  as.numeric(factor(df[,col]))-1
}
for(cat in cats) {
  data[,cat] <- encode(data,cat)
}
data$deposit <- as.factor(data$deposit)

```

### PCA

```{r}

i <- sample(1:150, 100, replace = FALSE)

train <- data[i,]
test <- data[-i,]

set.seed(2354)

pcaOut <- preProcess(train[,1:4], method = c("center", "scale", "pca"))
pcaOut

```

### PCA Plotting

```{r}

trainPc <- predict(pcaOut, train[, 1:4])
testPc <- predict(pcaOut, test[,])

plot(testPc$PC1, testPc$PC2, pch = c(23, 21, 22)[unclass(testPc$Species)], 
     bg = c("red", "green","blue")[unclass(test$Species)])

```



```{r}

trainDf <- data.frame(trainPc$PC1, trainPc$PC2, train$deposit)
testDf <- data.frame(testPc$PC1, testPc$PC2, test$deposit)

set.seed(2354)

pred <- knn(train = trainDf[,1:2], test = testDf[,1:2], cl = trainDf[,3], k = 3)
mean(pred == test$deposit)

```




```{r}

train <- subset(train, select = -c(contact, month, day, previous, poutcome, evr, 
                                   cpi, cci, euribor3m, employees))

colnames(trainDf) <- c("PC1", "PC2", "deposit")
colnames(testDf) <- c("PC1", "PC2", "deposit")

set.seed(2354)

tre <- tree(deposit~., data = trainDf)
plot(tre)
text(tre, cex = 0.5, pretty = 0)

pred <- predict(tre, newdata = testDf, type = "class")
mean(pred == test$deposit)

LD <- lda(deposit~., data = train)

```

### LDA

```{r}

LD <- lda(deposit~., data = train)

LD$means

```

### Predict on test

```{r}

LDpred <- predict(LD, newdata = test, type = "class")

mean(LDpred$class == test$deposit)

# output is too long

cat("Levels: 0 1")

```

### Plot

```{r}

plot(LDpred$x[,1], pch = c(23, 21, 22)[unclass(LDpred$class)],
     bg = c("red","green","blue")[unclass(testPc$deposit)])

```